Making Sequential Programs Deterministic

### 2019-04-06 design.tex
section 2 typos

The core of the determinism type system is the following type qualifiers:
\begin{itemize}
    \item \<NonDet> indicates
    that the expression might have different values in two different executions.
    \item \<OrderNonDet> indicates that the expression is a collection or
      map that contains the same elements in every execution, but possibly
      in a different order.
    \item \<Det> indicates that the expression evaluates to equal values in
      all executions; for a collection, iteration
      also yields the values in the same order.
\end{itemize}
\Cref{fig:typecheck-rules,fig:determinism-hierarchy} show the subtyping
relationship among the qualifiers.

@@

\noindent
would be instantiated at the least upper bound of the types of its first
and forth arguments, and the third argument must conform to the
instantiation.  However, the third argument does not affect the instantiation.

@@

It might seem that the notion of an order-nondeterministic set or map is
nonsensical, since the set and map specifications make no promises about
iteration order.  However, some subtypes do.
We explain why each of these is possible by considering three common
implementation strategies.

>>>>

The core of the determinism type system is the following type qualifiers:
\begin{itemize}
    \item \<NonDet> indicates
    that the expression might have different values in two different executions.
    \item \<OrderNonDet> indicates that the expression is a collection or
      a map that contains the same elements in every execution, but possibly
      in a different order.
    \item \<Det> indicates that the expression evaluates to equal values in
      all executions; for a collection, iteration
      also yields the values in the same order.
\end{itemize}
\Cref{fig:typecheck-rules,fig:determinism-hierarchy} show the subtyping
relationship among the qualifiers.

@@

\noindent
would be instantiated at the least upper bound of the types of its first
and fourth arguments, and the third argument must conform to the
instantiation.  However, the third argument does not affect the instantiation.

@@

It might seem that the notion of a deterministic set or map is
nonsensical, since the set and map specifications make no promises about
iteration order.  However, some subtypes do.
We explain why each of these is possible by considering three common
implementation strategies.
